Data Visualization

### 2018-11-09 papers/round_2_reviews.Rmd
Revision, Round 2, Iteration 2

---
title: "Round_2_Reviews"
author: "Andy Krause and Gideon Aschwanden"
date: "10/25/2018"
output: html_document
---

### Key Points:

@@

* ~~Add in something on Short term vs long term bonds~~
* ~~Doesn't trust hedonic estimation.  Do matched pairs.~~

* (in Progress) Can't determine who are actually investors, so the research question isn't valid
* ~~Make tables/figures self contained~~

### Full comments

@@

**As Real Estate is an asset class much like bonds there likely warrants a larger theoretical discussion on the short vs. long term holding structure.  However, we do not feel that this paper is the correct place to do so given its empirical focus.  The fact that this comment was raised (and the input from another reviewer regarding our research question) has led us to re-focus our research question and the aim of this study.  In short, we want to focus on the built environment side of the question, not the financial structuring side.  In other words, what types of properties in which locations are short term preferable, rather than attempting to make a judgement about the financial decision-making of an owner -- a situation whereby many individual and idiosyncratic factors play a large role  We appreciate you raising this concern as it has helped us think through the ultimate goal of our work.**

@@

**To address this issue we have added a 'matched-pairs'-type estimation to our imputation of long-term rents.  More specifically we do an ensemble of 3, 5, and 7 comparable matched-pairs type valuations using the nearest 3, 5, and 7 transactions that have identical bedrooms, bathrooms and structure type (apartment/detached). For apartments this often pulled in transactions in the same building, for detached dwelling on the same block or street. Results from this estimation show a 91% correlation with our hedonic results, though there did seem to be a deviation in the high end apartment market, especially for 1 bedroom units.  As a result, we take the average of the matched pairs ensemble and the hedonic model.**

@@

  ggplot(imp_df,
         aes(x=ltr_imp_revenueH, y=ltr_imp_revenueK, col = type)) + 
    geom_point(alpha = .5, size=.5) + 
    facet_grid(type ~ bed_lab) + 
    xlab('\nHedonic Revenue\n') + 
    ylab('Matched Pairs Revenue\n') + 
    theme(legend.position = 'none',
          plot.caption=element_text(hjust = 0.3),
          plot.title = element_text(hjust = 0.5)) +
    scale_color_manual(values = c('red', 'blue')) + 
    scale_x_continuous(breaks = c(15000, 30000, 45000),
                       labels = c('$15k', '$30k', '$45k'))+
    scale_y_continuous(breaks = c(15000, 30000, 45000),
                       labels = c('$15k', '$30k', '$45k'))+
    geom_abline(intercept = 0, slope = 1, linetype = 2,
                color = 'gray50') +
    labs(caption = fig_cap,
         title = 'Comparison of Hedonic and Matched Pairs Imputation')

@@

@@

* *Owner-occupiers*  **(Wait, what?  How do these factor in?  You can't occupy given our study design.)**
* *Vacation home owners* **(Our study design eliminates most of these give our boundary)**
* *Investors*

@@

**[Forthcoming] Discuss how our study design eliminated most vacation homes.  Move the Sensitive test on Maximizers to be the key focus of the paper**

@@

**[Forthcoming] Make a note about pivoting away from financial calculus to location/utility argument**

>>>>

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
subtitle: "Round 2 Reviews"
author: "Andy Krause and Gideon Aschwanden"
date: "11/8/2018"
output: pdf_document
---

### What's Changed

1. Refined sample to better fit research question
* Further focused on urban properties by removing rural homes from the sample due to likelihood of being second homes occasionally used by owners
* Removed all host types except "Profit Seekers" to minimize potential for remaining owner-occupiers and vacation homes in the sample

2. Added a 'matched-pairs' approach to long term rental imputation
* Blended with hedonic model to create an ensemble approach

3. Added two new sensitivity tests
* Examine the possible impacts of under estimates of short term costs
* Examine the possible impacts of over estimate of imputed long term rent estimates

4. Added captions to tables and figures to make them more self-contained

5. Updated title to represent change in focus

&nbsp;
&nbsp;
&nbsp;

### Direct responses to reviewers

&nbsp;
&nbsp;

@@

&nbsp;

@@

&nbsp;

**As Real Estate is an asset class much like bonds there likely warrants a larger theoretical discussion on the short vs. long term holding structure.  However, we do not feel that this paper is the correct place to do so given its empirical focus.  The fact that this comment was raised (and the input from another reviewer regarding our research question) has led us to re-focus our research question and pivot the aim of this study.  In short, we focus on the built environment side of the question, not the financial structuring side.  In other words, how do location, home characeristics and host policies impact short term preferability, rather than attempting to make a judgement about the financial decision-making of an owner -- a situation whereby many individual and idiosyncratic factors play a large role  We appreciate you raising this concern as it has helped us think through our research question and the ultimate goal of our work.**

&nbsp;

@@

&nbsp;

**To address this issue we have added a 'matched-pairs'-type estimation to our imputation of long-term rents.  More specifically we match homes based on structure type (apartment/detached), bedrooms and bathrooms and then take the median of the 7 nearest (geographically) comparables. For apartments this often pulled in transactions in the same building, for detached dwelling on the same block or street. Results from this estimation show a 89% correlation with our hedonic results, though there did seem to be a deviation in the high end apartment market, especially for 1 bedroom units.  As a result, we take the average of the matched pairs and the hedonic model estimates.**

&nbsp;

@@

  ggplot(imp_df,
         aes(x=ltr_imp_revenueH, y=ltr_imp_revenueK, col = type)) + 
    geom_point(alpha = .5, size=.5) + 
    facet_grid(type ~ bed_lab) + 
    xlab('\nHedonic Revenue\n') + 
    ylab('Matched Pairs Revenue (A$)\n') + 
    theme(legend.position = 'none',
          plot.caption=element_text(hjust = 0.3),
          plot.title = element_text(hjust = 0.5)) +
    scale_color_manual(values = c('red', 'blue')) + 
    scale_x_continuous(breaks = c(15000, 30000, 45000),
                       labels = c('$15k', '$30k', '$45k'))+
    scale_y_continuous(breaks = c(15000, 30000, 45000),
                       labels = c('$15k', '$30k', '$45k'))+
    geom_abline(intercept = 0, slope = 1, linetype = 2,
                color = 'gray50') +
    labs(caption = fig_cap,
         title = 'Comparison of Hedonic and Matched Pairs Imputation')

@@

&nbsp;
&nbsp;

@@

* *Owner-occupiers*  (**Eliminated via the 75% non-blocked filter**)
* *Vacation home owners*  (**Mostly eliminated via limiting to urbanized area**)
* *Investors*

@@

&nbsp;

**We have re-focused our sample, both geographically and by host behavior to attempt to elminate both Owner-Occupiers and Vacation Home owners.  Rather than working with this more limited sample of owners in a sensitivity test, we now focus the entire study on them.**

&nbsp;

@@

&nbsp;

**Thank you for the comment. We agree and we've altered our research question to focus the paper on to the spatial, structural and behavior (host policies) contributions to determining short term preference and away from the strict financial calculus of the decision of whether or not to Airbnb.**

&nbsp;

### 2018-11-09 scripts/5_data_viz.Rmd
Revision, Round 2, Iteration 2

@@

  png(filename = file.path(getwd(), 'images', "sub_loc_map.png"), 
       width = 6.5, height = 6.5, units = 'in', res = 300)

  tm_shape(suburb_sf) +
    tm_polygons("class", palette=c('gray20', 'gray50', 'gray80'), title='Suburb Class') +
  tm_shape(studyarea_sf) + 
    tm_borders(col='black', lwd=5) +
    tm_add_legend(type='fill', border.lwd=3, col='white', border.col='black',
                  title='Study Area')

@@

  sm_col <- c(col_df$rgb[3], col_df$rgb[4], col_df$rgb[5], 
              col_df$rgb[6], col_df$rgb[1])

  png(filename = file.path(getwd(), 'images', "ltr_loc_map.png"), 
       width = 4, height = 4, units = 'in', res = 300)
  tm_shape(studyarea_sf) + 
    tm_borders(col='gray50', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray90', lwd=.5) +
  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.3, shape=16, legend.col.show=TRUE)
  dev.off()

  png(filename = file.path(getwd(), 'images', "str_loc_map.png"), 
       width = 4, height = 4, units = 'in', res = 300)
  tm_shape(studyarea_sf) + 
    tm_borders(col='gray50', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray90', lwd=.5) +
  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.3, shape=16)
  dev.off()

@@

   # Make Airbnb submarket map

   strtype_bar <- ggplot() +
     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=sm_col, name='Submarket') +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Short Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

@@

   ltrtype_bar <- ggplot() +
     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=sm_col) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Long Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

@@

   ggplot(rev_df,
          aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=dens_cols) +
    scale_color_manual(values=dens_cols) +
    ggtitle('Revenue Comparison: Short Term vs Long Term Properties') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

  host.block.freq <- ggplot(str_tdf_all, aes(x=block_rate)) +
     geom_density(fill=str.col, color=str.col) +
     ylab('Frequency\n') +
     xlab('\n% of Time Property is Blocked') +
     scale_x_continuous(breaks=seq(0,1,.2),
                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
     #ggtitle('Host Block Rate Frequency\n') +
     theme(plot.title = element_text(hjust = 0.5)) +
     theme(axis.text.y=element_blank(),
           axis.ticks.y=element_blank())

  block.rate.period <- ggplot(str_tdf_all, aes(x=block_rate, y=nbr_block * (366/total_days))) +
    geom_point(fill=str.col, color=str.col, size=.2) +
    ylab('Nbr of Blocked Periods\n') +
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

 ggplot(str_tdf_all, aes(host_type, fill=host_type)) +
    geom_bar() +
    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[9]))+
    theme(legend.position='none') +
    ylab('Frequency\n') +
    xlab('\nHost Type') +
    scale_x_discrete(labels=c('Profit-Seekers','Opportunistic Sharers','Unknowns'))+
    #ggtitle('short-term Host Types') +
    theme(plot.title = element_text(hjust = 0.5))

>>>>

  inn_sf <- suburb_sf %>% dplyr::filter(class == 'Inner') %>% st_union()
  mid_sf <- suburb_sf %>% dplyr::filter(class == 'Middle' & 
                                          name != 'Seabrook' &  
                                           name != 'Altona Meadows') %>% st_union()

@@

  png(filename = file.path(getwd(), 'images', "sub_loc_map.png"), 
       width = 4.5, height = 4.5, units = 'in', res = 300)

  tm_shape(suburb_sf %>% dplyr::filter(class != 'Outer')) +
    tm_polygons("class", palette=c('gray50', 'gray80'), title='Suburb Class') +
  tm_shape(studyarea_sf) + 
    tm_borders(col='black', lwd=5) +
    tm_add_legend(type='fill', border.lwd=3, col='white', border.col='black',
                  title='Study Area')+
  tm_layout(
    legend.position = c("left","bottom"),
    legend.text.size = 0.5)

@@

  sm_col <- c(col_df$rgb[3], col_df$rgb[4], col_df$rgb[5], 
              col_df$rgb[6])

  ltr_map <-   tm_shape(mid_sf) + 
    tm_fill(col='gray95', lwd=1) +
  tm_shape(inn_sf) + 
    tm_fill(col='gray90', lwd=1) +
  tm_shape(studyarea_sf) + 
    tm_borders(col='black', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray80', lwd=.5) +
  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.9, shape=16, legend.col.show=TRUE)+
    tm_layout(title = "LTR Observations",
              title.position = c("center", "top"),
              title.size = .8)

  str_map <- tm_shape(mid_sf) + 
    tm_fill(col='gray95', lwd=1) +
  tm_shape(inn_sf) + 
    tm_fill(col='gray90', lwd=1) +
  tm_shape(studyarea_sf) + 
    tm_borders(col='black', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray80', lwd=.5) +
  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.9, shape=16) + 
    tm_layout(title = "STR Observations",
              title.position = c("center", "top"),
              title.size = .8)

  sltr_map <- tmap_arrange(ltr_map, str_map)

  png(filename = file.path(getwd(), 'images', "ltr_loc_map.png"), 
       width = 7, height = 3.5, units = 'in', res = 300)
    sltr_map
  dev.off()

@@

   # Make Airbnb submarket map
   str_tdf$Submarket <- as.character(str_tdf$geo_mrkt)
   str_tdf$Submarket[str_tdf$Submarket == 'city-core'] <- '   City-Core   '
   str_tdf$Submarket[str_tdf$Submarket == 'city'] <- '   City   '
   str_tdf$Submarket[str_tdf$Submarket == 'beach'] <- '   Beach   '
   str_tdf$Submarket[str_tdf$Submarket == 'suburban'] <- '   Suburban   '
   str_tdf$Submarket <- factor(str_tdf$Submarket, 
                                  levels = c('   City-Core   ', '   City   ', 
                                             '   Suburban   ', '   Beach   '))

   strtype_bar <- ggplot() +
     geom_bar(data=str_tdf, aes(x=Submarket, fill=Submarket)) +
     scale_fill_manual(values=sm_col, name='Submarket') +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'none',
           legend.title = element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Short Term Properties')+
     theme(plot.title = element_text(size = 10, hjust = 0.5),
           axis.text.y=element_blank(),
           axis.text.x=element_text(size = 6),
           axis.ticks.y=element_blank(),
           plot.caption=element_text(size=6, hjust=.5)) + 
     labs(caption = paste0('\nBreakdown of 2,415 short-term properties by submarket and ',
                           ' structure type.\n'))
  # strtype_bar

@@

   ltr_tdf$Submarket <- as.character(ltr_tdf$geo_mrkt)
   ltr_tdf$Submarket[ltr_tdf$Submarket == 'city-core'] <- '   City-Core   '
   ltr_tdf$Submarket[ltr_tdf$Submarket == 'city'] <- '   City   '
   ltr_tdf$Submarket[ltr_tdf$Submarket == 'beach'] <- '   Beach   '
   ltr_tdf$Submarket[ltr_tdf$Submarket == 'suburban'] <- '   Suburban   '
   ltr_tdf$Submarket <- factor(ltr_tdf$Submarket, 
                                  levels = c('   City-Core   ', '   City   ', 
                                             '   Suburban   ', '   Beach   '))
   ltrtype_bar <- ggplot() +
     geom_bar(data=ltr_tdf, aes(x=Submarket, fill=Submarket)) +
     scale_fill_manual(values=sm_col) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'none',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Long Term Properties')+
     theme(plot.title = element_text(size = 10, hjust = 0.5),
           axis.text.y=element_blank(),
           axis.text.x=element_text(size = 6),
           axis.ticks.y=element_blank(),
           plot.caption=element_text(size=6, hjust=.5)) + 
     labs(caption = paste0('\nBreakdown of 64,305 long-term properties by submarket and ',
                           ' structure type\n'))
     #ltrtype_bar

@@

   ggplot(rev_df,
          aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=dens_cols) +
    scale_color_manual(values=dens_cols) +
    # ggtitle('Revenue Comparison: Short Term vs Long Term Properties') +
    xlab('Annual Revenue (A$)') +
    ylab('')+
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('A$0', 'A$20,000', 'A$40,000', 'A$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank())+
     theme(plot.title = element_text(size = 10, hjust = 0.5),
           axis.text.y=element_blank(),
           axis.text.x=element_text(size = 6),
           axis.ticks.y=element_blank(),
           plot.caption=element_text(size=6, hjust=0)) + 
     labs(caption = paste0('\nComparison of the distribution of observed long-term rental',
                           ' revenues of 64,305 properties (blue) to observed revenues of ', 
                           ' 2,415 short\nterm properties (pink).  The purple curve ',
                           ' represents the potential revenues of the 2,415 short term ',
                           ' properties (includes imputed bookings).')) +
    coord_cartesian(xlim=c(0, 70000))

@@

  host.block.freq <- ggplot(str_tdf_all, aes(x=block_rate)) +
     geom_density(fill=str.col, color=str.col) +
     ylab('Frequency\n') +
     xlab('\n\n% of Time Property is Blocked') +
     scale_x_continuous(breaks=seq(0,1,.2),
                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
     #ggtitle('Host Block Rate Frequency\n') +
     theme(plot.title = element_text(hjust = 0.5, size = 10)) +
     theme(axis.text.y=element_blank(),
           axis.ticks.y=element_blank(),
           plot.caption=element_text(size=6, hjust=0)) + 
     labs(caption = paste0('\nDensity plot of frequency of blocking schedule for short term ',
                           '\nleasing observations. Blocking indicates that the property ',
                           'is \nnot available for nightly rental on Airbnb. Vertical lines',
                           '\ndelineate the three host type groupings.'),
          title = 'Host Blocking Frequency\n') +
    geom_vline(xintercept = .25, linetype="dashed", color = "black", size=.5, alpha=.5)+
    geom_vline(xintercept = .75, linetype="dashed", color = "black", size=.5, alpha=.5)

  block.rate.period <- ggplot(str_tdf_all, 
                              aes(x=block_rate, y=nbr_block * (366/total_days))) +
    geom_point(fill=alpha(str.col,.3), color=alpha(str.col,.3), size=.1, shape=16) +
    ylab('Nbr of Blocked Periods\n') +
    xlab('\n\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
     theme(plot.title = element_text(size = 10, hjust = 0.5),
           axis.text.y=element_blank(),
           axis.ticks.y=element_blank(),
           plot.caption=element_text(size=6, hjust=0)) + 
     labs(caption = paste0('\nCumulative time of blocking for short term properties ',
                           '(x-axis) \nversus the total number of periods where the ',
                           'property was \nblocked from nightly rental.',
                           'Vertical lines delineate the three \nhost type groupings.'),
          title = 'Block Rate vs Blocked Periods\n')+
    geom_vline(xintercept = .25, linetype="dashed", color = "black", size=.5, alpha=.5)+
    geom_vline(xintercept = .75, linetype="dashed", color = "black", size=.5, alpha=.5)

@@

 ggplot(str_tdf_all, aes(host_type, fill=host_type)) +
    geom_bar() +
    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[9]))+
    theme(legend.position='none') +
    ylab('') +
    xlab('') +
    scale_x_discrete(labels=c('Profit-Seekers','Opportunistic Sharers','Unknowns'))+
    # ggtitle('short-term Host Types') +
     theme(plot.title = element_text(size = 10, hjust = 0.5),
           axis.text.y=element_blank(),
           axis.text.x=element_text(size = 6),
           axis.ticks.y=element_blank(),
           plot.caption=element_text(size=6, hjust=0)) + 
     labs(caption = paste0('\nBreakdown of Host Types for Short Term Properties:\n\n',
                           '1) Profit Seekers:               <= 25% Blocked             3,056 Obs.\n',
                           '2) Opportunistic Sharers:   >= 75% Blocked             1,743 Obs.\n',
                           '3) Unknowns:                     25% > 75% Blocked       2,707 Obs.\n')) + 
   annotate("text", x = 1, y = 3300, label = "41%") +
   annotate("text", x = 2, y = 2000, label = "23%") +
   annotate("text", x = 3, y = 2949, label = "36%") +
   coord_cartesian(ylim=c(0,3500))
